Supporting Awareness of Indirect Conflicts with Impact

### 2013-06-05 impact-position-2013/paper.tex
Added missing Meyer reference.

In this paper, we report on our research into supporting indirect conflicts
and present the design, implementation, and future evaluation of the tool \textit{Impact},
a web based tool that aims at detecting indirect conflicts among developers
and notifying the appropriate members involved in these conflicts.
By leveraging technical relationships inherent of 
software projects with method call graphs~\cite{Lakhotia:1993:CCM}
as well as detecting changes
to these technical relationship through software configuration management
(SCM) systems, \textit{Impact} is able to detect indirect conflicts as well as
alert developers involved in such conflicts in task awareness while limiting information
overload by using design by contract~\cite{} solutions to method design. While this paper
outlines \textit{Impact's} specific implementation, its design is rather
generic and can be implemented in similar indirect conflict awareness tools.
\textit{Impact} represents a first step towards the design and implementation
of awareness tools which address indirect conflicts in software development.

@@

\section{Proposed Solution to Information Overload}
\label{sec:ns}
As was previously stated, the main issue to be addressed with Impact is
information overload. Our potential solution comes from the ideas of
Myers~\cite{} on ``design by contract''. In this methodology, changes to method
preconditions and postconditions are considered to be the most harmful. 
This includes adding conditions that must be met by both input
and output parameters such as limitations to input and expected
output. To achieve this level of source code analysis, the ideas of
Fluri et al.~\cite{Fluri:2007:CDT} can be used on the previously generated
ASTs for high granularity
source code change extraction when determining if preconditions or
postconditions have changed.
We plan to bring these ideas into the realm of what makes a
change ``notification worthy'', as to deal with information overload for
developers using Impact. By only examining ``notification worthy'' changes,
Impact would cut down the number of notifications 
issued to just those which developers care about. To investigate this solution, we plan to
interview and survey industry software developers at a wide range of
experience to determine what makes a change in software important. We believe
by only monitoring what developers and Myers~\cite{} find important to
indirect conflict awareness, we will be able to eliminate information overload
in Impact and other dependency awareness tools. We believe that these preconditions
and postconditions will serve as the main tool for dealing with information overload.

>>>>

In this paper, we report on our research into supporting indirect conflicts
and present the design, implementation, and future evaluation of the tool \textit{Impact},
a web based tool that aims at detecting indirect conflicts among developers
and notifying the appropriate members involved in these conflicts.
By leveraging technical relationships inherent of 
software projects with method call graphs~\cite{Lakhotia:1993:CCM}
as well as detecting changes
to these technical relationship through software configuration management
(SCM) systems, \textit{Impact} is able to detect indirect conflicts as well as
alert developers involved in such conflicts in task awareness while limiting information
overload by using design by contract~\cite{Meyer:1988} solutions to method design. While this paper
outlines \textit{Impact's} specific implementation, its design is rather
generic and can be implemented in similar indirect conflict awareness tools.
\textit{Impact} represents a first step towards the design and implementation
of awareness tools which address indirect conflicts in software development.

@@

\section{Proposed Solution to Information Overload}
\label{sec:ns}
As was previously stated, the main issue to be addressed with Impact is
information overload. Our potential solution comes from the ideas of
Meyer~\cite{Meyer:1988} on ``design by contract''. In this methodology, changes to method
preconditions and postconditions are considered to be the most harmful. 
This includes adding conditions that must be met by both input
and output parameters such as limitations to input and expected
output. To achieve this level of source code analysis, the ideas of
Fluri et al.~\cite{Fluri:2007:CDT} can be used on the previously generated
ASTs for high granularity
source code change extraction when determining if preconditions or
postconditions have changed.
We plan to bring these ideas into the realm of what makes a
change ``notification worthy'', as to deal with information overload for
developers using Impact. By only examining ``notification worthy'' changes,
Impact would cut down the number of notifications 
issued to just those which developers care about. To investigate this solution, we plan to
interview and survey industry software developers at a wide range of
experience to determine what makes a change in software important. We believe
by only monitoring what developers and Meyer~\cite{Meyer:1988} find important to
indirect conflict awareness, we will be able to eliminate information overload
in Impact and other dependency awareness tools. We believe that these preconditions
and postconditions will serve as the main tool for dealing with information overload.
